### 2022-05-27 main/chapter_2ljets.tex
change tq to Zg, remove -and their features

\section{Events and their features}
From its name, the $\twoljets$ analysis analyses features of events with two
charged leptons (electrons or muons --- not taus), and at least one jet.
Though not nominal, the a $\met$ requirement is also implicit from the context
of $R$-parity conserving supersymmetric models.
This section serves to describe how events are selected for the $\twoljets$
analyses, and which event variables are extracted for use in its selections.

@@

The magnitude of $\ptmiss$ is $\met$, pronounced `met'.
Please note that $\met$ is not an energy.
Transverse energy does not exist.
One may of course define their own directed `transverse energy', but it will
not be conserved (in the standard model) unless it is equivalent to a conserved
momentum.
Indeed, momentum-balanced events do have energy imbalances;
for example, in a single-top event $pp \rightarrow tq$, the $t$ and $q$ are
produced back-to-back with equal momenta $p$, but the two particles have very
different energies since they have very different masses:
$E_t^2 = m_t^2 + p^2$, $E_q^2 = m_q^2 + p^2$, and $m_t \gg m_q$.
% hobbyhorse

>>>>

\section{Events}
From its name, the $\twoljets$ analysis analyses features of events with two
charged leptons (electrons or muons --- not taus), and at least one jet.
Though not nominal, the a $\met$ requirement is also implicit from the context
of $R$-parity conserving supersymmetric models.
This section serves to describe how events are selected for the $\twoljets$
analyses, and which event variables are extracted for use in its selections.

@@

The magnitude of $\ptmiss$ is $\met$, pronounced `met'.
Please note that $\met$ is not an energy.
Transverse energy does not exist.
One may of course define their own directed `transverse energy', but it will
not be conserved (in the standard model) unless it is equivalent to a conserved
momentum.
Indeed, momentum-balanced events do have energy imbalances;
for example, in a $Z\mathrm{+jet}$ event $pp \rightarrow Zg$, the $Z$ and $g$
are produced back-to-back with equal momenta $p$, but the two particles have
very different energies since they have very different masses:
$E_Z^2 = m_Z^2 + p^2$, $E_g^2 = 0 + p^2$.
% hobbyhorse
